# Code Access 

The code you use to produce analytical outcomes and summaries is the lifeblood of your work as a data science practitioner.  

Literate programming platforms provide unique tools for code access that are enabled at the document/presentation-level, if desired. For example, you may have collaborators who wish to inspect code or you may be documenting your code to provide full transparency to the process(es) used to conduct an analysis.

## Code sharing

The code represented in @lst-first (and all example pieces of code) can be copied by activating the clipboard option in the upper-right hand corner of the code chunk. 

::: {.callout-tip .column-margin}
Code can always be copied onto your personal computer via the clipboard icon: `r fontawesome::fa("clipboard")`. 
:::

```{r}
#| lst-label: lst-first
#| lst-cap: Addition within `R`
#| echo: true
#| output: false
1 + 1                                    

```

For more complex bits of analysis, hidden annotations are available (the reader can further access notes/assistance by hovering over the circled numbers):

```{r}
#| lst-label: lst-second
#| code-annotations: true


library(psych)               # <1>
data(bfi)                    # <2>

bfi$jibberish <- rowMeans(bfi[1:10], na.rm=TRUE)       # <3>
bfi$gobbleyjook <- rowMeans(bfi[11:20], na.rm=TRUE)    # <3>

```

1. The `psych` package contains example data that we can access.
2. This gives us access to the `bfi` dataset that contains personality item responses.
3. We make 2 scale scores, `jibberish` and `gobbleyjook`. The `$` notation indicates that these scale scores will be appended to the `bfi` dataframe.

The entire code block can also be hidden unless asked-for. These features permit reviewers/collaborators of different need or curiosity to access source code on an as-needed basis:

```{r}
#| lst-label: lst-three
#| code-fold: true

library(psych)               # <1>
data(bfi)                    # <2>

bfi$jibberish <- rowMeans(bfi[1:10], na.rm=TRUE)       # <3>
bfi$gobbleyjook <- rowMeans(bfi[11:20], na.rm=TRUE)    # <3>

```
1. The `psych` package contains example data that we can access.
2. This gives us access to the `bfi` dataset that contains personality item responses.
3. We make 2 scale scores, `jibberish` and `gobbleyjook`. The `$` notation indicates that these scale scores will be appended to the `bfi` dataframe.
